BetweenExpDifferences

### 2016-03-17 analysis/BetweenExpDifferences.Rmd
added section - comparing non-compliant vs compliant literal listener data.

>>>>

### Save non-compliant
```{r}
allL0ListenerNC <- rbind(e8, e10, e12) %>%
  subset(scale != "training1" & scale != "training2")
allL0ListenerNC$exp <- as.factor(allL0ListenerNC$exp)
## judgment :: numeric
allL0ListenerNC$judgment <- as.numeric(allL0ListenerNC$judgment) 
allL0ListenerNC$stars <- as.numeric(as.character(allL0ListenerNC$stars)) / 20

ne8 <- allL0ListenerNC %>%
  filter(exp == "e8") %>%
  group_by(workerid) %>%
  summarise(n = 1) %>%
  nrow()
ne10 <- allL0ListenerNC %>%
  filter(exp == "e10") %>%
  group_by(workerid) %>%
  summarise(n = 1) %>%
  nrow()
ne12 <- allL0ListenerNC %>%
  filter(exp == "e12") %>%
  group_by(workerid) %>%
  summarise(n = 1) %>%
  nrow()

literalD_NC <- allL0ListenerNC %>%
  group_by(exp, scale, degree, stars) %>%
  summarise(cnt.judgment = sum(judgment))
literalD_NC$speaker.p <- with(literalD_NC,
                           ifelse(exp == "e8", cnt.judgment / ne8,
                                  ifelse(exp == "e10",
                                         cnt.judgment / ne10, cnt.judgment / ne12)))
literalD_NC$exp <- as.character(literalD_NC$exp)
literalD_NC$words <- mapply(lookupScalar, literalD_NC$degree, literalD_NC$scale, literalD_NC$exp)
drop <- c("cnt.judgment", "degree")
literalD_NC <- literalD_NC[, !(names(literalD_NC) %in% drop)]

# normalize for comparison
for (e in unique(literalD_NC$exp)) {
  for (word in unique(literalD_NC$words)) {
    literalD_NC[literalD_NC$words == word & literalD_NC$exp == e, "speaker.p"] <-
      rrrsa::rsa.normVec(subset(literalD_NC, words == word & exp == e)$speaker.p)
  }
}

subset(literalD_NC, words == "excellent" & exp == "e12")
subset(peloquinFrank_4Alts, words == "excellent")
rrrsa::rsa.normVec(subset(speakerL12, scale == "good_excellent" & degree == "hi1")$speaker.p)

```
